DESIGN OF A TWO-PIECE BRASSIERE CUP TO FIT BREAST DATA POINTS TOWARD ITS AUTOMATION

### 2021-01-18 template/paper/paper_e.tex
20210119

\author{Kotaro {\sc Yoshida}${}^\dagger$, Hidefumi {\sc Wakamatsu}${}^\dagger$, Eiji {\sc Morinaga}${}^\ddagger$, and Takahiro {\sc Kubo}${}^\S$}

@@

This section explains the numerical expressions of a developable surface. The curvature of a space curve on a surface can be divided into two: the normal curvature and geodesic curvature. The former is realized by deforming the surface, while the latter is realized by deforming a space curve. Deforming the surface does not change the geodesic curvature as long as the surface is not stretched. In the case of a brassiere cup, only the normal curvature can be manipulated by deforming the surface. Because the geodesic curvature cannot be manipulated by deforming the surface, it must be designed such that the space curve coincides with a boundary of the developable surface. 
Here, we propose a method to determine a developable surface using two curves that lie on the surface and design a pattern shape. Consider the case where the \textit{lower edge} is the curve connecting the lower wire (\rfig{fig:pattern_L}) and the \textit{upper edge} is that combining the upper cup (\rfig{fig:pattern_U}). Our method expresses the developable surface using the parameters of a space curve, the condition of two lines that lie on the developable surface, and their obtained pattern shape. \rfig{fig:obj_coord} depicts the object coordinate system on the lower edge of the cup surface, where the $\zeta$-axis always coincides with the tangential direction of the edge line and the  $ \eta $-axis always coincides with the surface normal direction. Deformation of the cup changes the posture of the object coordinate system. Thus, the infinitesimal displacement vector of each axial direction can be described by the infinitesimal rotational ratio vector $ \mbold{\omega} = \left[\omega_{\xi}\;\;\omega_{\eta}\;\;\omega_{\zeta}\right]^{\mathrm{T}}$ as

@@

	\includegraphics[width = \columnwidth]{./figure/PatternImage2.eps}

@@

\rfig{fig:ObtainedSurfaceDS} shows the obtained shape and input data for Case (1), where the solid line represents the given wire line. Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.  \rfig{fig:ObtainedSurfaceDS_Pat} shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively.
Next, a uniform random number was generated by numpy.random() of Python. \rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (2). \rtab{tbl:error and calc_Example} shows the error and calculation time of case(1) and (2).
\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|} \hline
		-& Error & Time[sec] \\ \hline
		case(1) & 0.10 & 1802 \\ \hline
		case(2) & 0.12 & 740 \\ \hline
	\end{tabular}
	\caption{The error and calculation time of our proposed method in case(1) and (2).}
	\label{tbl:error and calc_Example}
\end{table}
For this result, we confirm that our proposed method can recreate a given shape as a two-piece brassire cup and approximate an undevelopable surface.

\subsection*{Experimental Verification}
For confirming the verification, we measured a breast shape of the torso, which is a typical breast shape, and apply our proposed method to it. A wire line is the same as \req{eq:vrf_omgW}, and the connection point is given as 
\begin{equation}\label{eq:givenXc2}
	\mbold{X}_C = \left[ \begin{array}{ccc}
	0.2 & 0.41 & 0.27
	\end{array}\right]^\mathrm{T}.
\end{equation}
In measured the entire shape of a torso, we used the measured point cloud that satisfies $ y \leq 0.2 $ as shown in \rfig{fig:Border}

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\columnwidth]{./figure/Measure/SetLine.png}
	\caption{The border line to use a point cloud in the experiment.}
	\label{fig:Border}
\end{figure}  
\chcolor{The simulations aim to confirm that the propose method whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” .\rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data of experiments,  \rfig{fig:ObtainedSurfaceNDS2_Pat} shows the obtained pattern. In \rfig{fig:ObtainedSurfaceNDS2} and \rfig{fig:ObtainedSurfaceNDS2_Pat}, we set $ L_M = 72.8$. } \chcolor{\rtab{tbl:error and calc2} shows the error and calculation time of the experiment. From the result, we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.
Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.}
\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|} \hline
		Error & Time[sec] \\ \hline
		1.04& 1682 \\ \hline
	\end{tabular}
	\caption{The error and calculation time of the proposed method in experiment.}
	\label{tbl:error and calc2}
\end{table}

\begin{figure}[h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-x.png}
		\label{fig:zx-DS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-y.png}
		\label{fig:zy-DS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromx-y.png}
		\label{fig:xy-DS}
	}
	\caption{Obtained shape and input data points in Case(2)}
	\label{fig:ObtainedSurfaceDS}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[Lower pattern]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternL.png}
		\label{fig:low-DS}
	}
	\hfil
	\subfigure[Upper pattern]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedPatternU.png}
		\label{fig:upp-DS}
	}
	\caption{Obtained patterns in Case(1)}
	\label{fig:ObtainedSurfaceDS_Pat}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth,clip]{./figure/NDS/ObtainedRidgeLinefromz-x.png}
		\label{fig:zx-NDS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromz-y.png}
		\label{fig:zy-NDS}
	}
	\hfil
	\subfigure[xy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromx-y.png}
		\label{fig:xy-NDS}
	}
	\caption{Obtained shape and input data points in Case(2)}
	\label{fig:ObtainedSurfaceNDS}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[Lower pattern]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternL.png}
		\label{fig:low-NDS}
	}
	\hfil
	\subfigure[Upper pattern]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternU.png}
		\label{fig:upp-NDS}
	}

@@

\begin{figure}[H]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromz-x.png}
		\label{fig:zx-NDS2}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromz-y.png}
		\label{fig:zy-NDS2}
	}
	\hfil
	\subfigure[xy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromx-y.png}
		\label{fig:xy-NDS2}
	}
	\caption{Obtained shape and input data points in the experiment}
	\label{fig:ObtainedSurfaceNDS2}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[Lower pattern]{
		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedPatternL.png}
		\label{fig:low-NDS2}
	}
	\hfil
	\subfigure[Upper pattern]{
		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedPatternU.png}
		\label{fig:upp-NDS2}
	}

@@

@@

\authorbiography{Kotaro, YOSHIDA}{}{Non-Member}{%
	Kotaro Yoshida received his B.Eng. and M.Eng. degree from Osaka University in 2017 and 2019, respectively. He is doing a doctoral degree at Osaka University.
}

\authorbiography{Hidefumi, ,WAKAMATSU}{}{Member}{%
	HidefumiWakamatsu received his B.Eng.,
	M.Eng. and Ph.D. degrees from Osaka
	University, Japan, in 1993, 1994 and
	2001, respectively. From 1995 to 2006,
	he worked as a Research Associate, Osaka
	University. He then became an Associate
	Professor at Division of Materials and Manufacturing
	Science, Osaka University. His research interests
	include handling of flexible object. He is a member of
	RSJ, JSME, JSPE, JWS and TMSJ.
}

\authorbiography{Eiji, ,MORINAGA}{}{Member}{%
	Eiji Morinaga received his B.Eng., M.Eng.
	and Ph.D. degrees in Mechanical Engineering
	from Osaka University, Japan,
	in 2000, 2002 and 2005, respectively. From
	2005 to 2007, he worked as a Designated
	Researcher at Center for Advanced Science
	and Innovation, Osaka University. He then became
	an Assistant Professor at Division of Materials and Manufacturing
	Science, Osaka University. His research interests
	include system design and integration in product design
	and manufacturing. He is a member of JSME, JSPE,
	JWS, JIEP and TMSJ.
}

\authorbiography{Takahiro, ,KUBO}{}{Non-Member}{%
	Takahiro Kubo received his B.A. degree in Sport Sciences from Waseda University, Japan, in 2007, and M.A. degree in Arts and Sciences from Tokyo University, Japan, in 2010. He then joined Wacoal Corp. His position is in Human Science Research Center.
}

>>>>

\author{Kotaro {\sc Yoshida}${}^\dagger$, Hidefumi {\sc Wakamatsu}${}^\dagger$, Eiji {\sc Morinaga}${}^\ddagger$,  Seichiro {\sc Tsutsumi}${}^\S$, Takahiro {\sc Kubo}${}^\P$}

@@

This section explains the numerical expressions of a developable surface. The curvature of a space curve on a surface can be divided into two: the normal curvature and geodesic curvature. The former is realized by deforming the surface, while the latter is realized by deforming a space curve. Deforming the surface does not change the geodesic curvature as long as the surface is not stretched. In the case of a brassiere cup, only the normal curvature can be manipulated by deforming the surface. Because the geodesic curvature cannot be manipulated by deforming the surface, it must be designed such that the space curve coincides with a boundary of the developable surface. 
Here, we propose a method to determine a developable surface using two curves that lie on the surface and design a pattern shape. Consider the case where the \textit{lower edge} is the curve connecting the lower wire (\rfig{fig:patterns}(b)) and the \textit{upper edge} is that combining the upper cup (\rfig{fig:patterns}(a)). Our method expresses the developable surface using the parameters of a space curve, the condition of two lines that lie on the developable surface, and their obtained pattern shape. \rfig{fig:obj_coord} depicts the object coordinate system on the lower edge of the cup surface, where the $\zeta$-axis always coincides with the tangential direction of the edge line and the  $ \eta $-axis always coincides with the surface normal direction. Deformation of the cup changes the posture of the object coordinate system. Thus, the infinitesimal displacement vector of each axial direction can be described by the infinitesimal rotational ratio vector $ \mbold{\omega} = \left[\omega_{\xi}\;\;\omega_{\eta}\;\;\omega_{\zeta}\right]^{\mathrm{T}}$ as

@@

	\includegraphics[width = \columnwidth]{./figure/PatternImage2.png}

@@

\rfig{fig:ObtainedSurfaceDS} shows the obtained shape and input data for Case (1), where the solid line represents the given wire line. Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.  \rfig{fig:ObtainedSurfaceDS_Pat} shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively.
Next, a uniform random number was generated by numpy.random() of Python. \rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (2). \rtab{tbl:error and calc_Example} shows the error and calculation time of case(1) and (2).

\begin{figure}[!h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-x.png}
		\label{fig:zx-DS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-y.png}
		\label{fig:zy-DS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromx-y.png}
		\label{fig:xy-DS}
	}
	\caption{Obtained shape and input data points in Case(2)}
	\label{fig:ObtainedSurfaceDS}
\end{figure}

\begin{figure}[!h]
	\centering
	\subfigure[Lower pattern]{
		\includegraphics[width=0.8\columnwidth]{./figure/DS/ObtainedPatternL.png}
		\label{fig:low-DS}
	}
	\hfil
	\subfigure[Upper pattern]{
		\includegraphics[width=0.8\columnwidth]{./figure/DS/ObtainedPatternU.png}
		\label{fig:upp-DS}
	}
	\caption{Obtained patterns in Case(1)}
	\label{fig:ObtainedSurfaceDS_Pat}
\end{figure}

\begin{figure}[!h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth,clip]{./figure/NDS/ObtainedRidgeLinefromz-x.png}
		\label{fig:zx-NDS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromz-y.png}
		\label{fig:zy-NDS}
	}
	\hfil
	\subfigure[xy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromx-y.png}
		\label{fig:xy-NDS}
	}
	\caption{Obtained shape and input data points in Case(2)}
	\label{fig:ObtainedSurfaceNDS}
\end{figure}

\begin{figure}[!h]
	\centering
	\subfigure[Lower pattern]{
		\includegraphics[width=0.8\columnwidth]{./figure/NDS/ObtainedPatternL.png}
		\label{fig:low-NDS}
	}
	\hfil
	\subfigure[Upper pattern]{
		\includegraphics[width=0.8\columnwidth]{./figure/NDS/ObtainedPatternU.png}
		\label{fig:upp-NDS}
	}

@@

\begin{table}[h]
	\centering
	\caption{The error and calculation time of our proposed method in case(1) and (2).}
	\label{tbl:error and calc_Example}
	\begin{tabular}{|c|c|c|} \hline
		-& Error & Time[sec] \\ \hline
		case(1) & 0.10 & 1802 \\ \hline
		case(2) & 0.12 & 740 \\ \hline
	\end{tabular}
\end{table}
For this result, we confirm that our proposed method can recreate a given shape as a two-piece brassire cup and approximate an undevelopable surface.

\subsection*{Experimental Verification}
For confirming the verification, we measured a breast shape of the torso, which is a typical breast shape, and apply our proposed method to it. A wire line is the same as \req{eq:vrf_omgW}, and the connection point is given as 
\begin{equation}\label{eq:givenXc2}
	\mbold{X}_C = \left[ \begin{array}{ccc}
	0.2 & 0.41 & 0.27
	\end{array}\right]^\mathrm{T}.
\end{equation}
\chcolor{In measured the entire shape of a torso, we assumed the measured point cloud covered by a brassiere cup that satisfies $ y \leq 0.2 $ as shown in \rfig{fig:Border}}

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\columnwidth]{./figure/Measure/SetLine.png}
	\caption{The border line to use a point cloud in the experiment,}
	\label{fig:Border}
\end{figure}
\chcolor{where we set $ L_M = 72.8$ in order to convert milimeter into centimenter and set the wire line as  \req{eq:vrf_omgW}. The simulations aim to confirm that the propose method whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” .\rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data of experiments,  \rfig{fig:ObtainedSurfaceNDS2_Pat} shows the obtained pattern.} \chcolor{\rtab{tbl:error and calc2} shows the error and calculation time of the experiment. From the result, we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.
Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.}

\begin{figure}[!h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromz-x.png}
		\label{fig:zx-NDS2}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromz-y.png}
		\label{fig:zy-NDS2}
	}
	\hfil
	\subfigure[xy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/Measure/ObtainedRidgeLinefromx-y.png}
		\label{fig:xy-NDS2}
	}
	\caption{Obtained shape and input data points in the experiment}
	\label{fig:ObtainedSurfaceNDS2}
\end{figure}

\begin{figure}[!h]
	\centering
	\subfigure[Lower pattern]{
		\includegraphics[width=0.8\columnwidth]{./figure/Measure/ObtainedPatternL.png}
		\label{fig:low-NDS2}
	}
	\hfil
	\subfigure[Upper pattern]{
		\includegraphics[width=0.8\columnwidth]{./figure/Measure/ObtainedPatternU.png}
		\label{fig:upp-NDS2}
	}

@@

\begin{table}[!h]
	\centering
	\caption{The error and calculation time of the proposed method in experiment.}
	\label{tbl:error and calc2}
	\begin{tabular}{|c|c|} \hline
		Error & Time[sec] \\ \hline
		1.04& 1682 \\ \hline
	\end{tabular}
\end{table}

@@

\authorbiography{Kotaro, YOSHIDA}{}{Non-Member}{%
	Kotaro Yoshida received his B.Eng. and M.Eng. degree from Osaka University in 2017 and 2019, respectively. He is currently pursuing a doctoral degree at Osaka University.
}

\authorbiography{Hidefumi, ,WAKAMATSU}{}{Member}{%
	HidefumiWakamatsu received his B.Eng.,
	M.Eng. and Ph.D. degrees from Osaka
	University, Japan, in 1993, 1994 and
	2001, respectively. From 1995 to 2006,
	he worked as a Research Associate, Osaka
	University. In 2007, he was appointed as 
	Professor at Division of Materials and Manufacturing
	Science, Osaka University. His research interests
	include handling of flexible object. He is a member of
	RSJ, JSME, JSPE, JWS and TMSJ.	
}

\authorbiography{Eiji, ,MORINAGA}{}{Member}{%
	Eiji Morinaga received his B.Eng., M.Eng.
	and Ph.D. degrees in Mechanical Engineering
	from Osaka University, Japan,
	in 2000, 2002 and 2005, respectively. From
	2005 to 2007, he worked as a Designated
	Researcher at Center for Advanced Science
	and Innovation, Osaka University. In 2007, he appointed as 
	an Assistant Professor at Division of Materials and Manufacturing
	Science, Osaka University. His research interests
	include system design and integration in product design
	and manufacturing. He is a member of JSME, JSPE,
	JWS, JIEP and TMSJ.
}

\authorbiography{Seiichiro, ,TSUTSUMI}{}{Non-Member}{%
	Seiichiro Tsutsumi received his B.Eng., M.Eng., Ph.D.(Agr.) and  
	Ph.D.(Eng.) degrees from Kyushu University, Japan, in 1997, 1999, 2002  
	and 2007, respectively. He worked as a Assistant Professor at Tohoku  
	University and Kyushu University from 2002 and 2004, respectively. He  
	then joined at Joining and Welding Research Institute, Osaka University  
	from 2011 as an Associate Professor. His research interests include  
	plasticity and fracture of solids. He is a member of JWS, JSCE, JSME,  
	JASNAOE, etc.
}

\authorbiography{Takahiro, ,KUBO}{}{Non-Member}{%
	Takahiro Kubo received his B.A. degree in Sport Sciences from Waseda University, Japan, in 2007, and M.A. degree in Arts and Sciences from Tokyo University, Japan, in 2010. In 2010, he joined Wacoal Corp and works at the Human Science Research Center.
}
